Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-08-12 Latex_files/Thesis/chapters/chapter 4/main.tex
updates to ch3

\paragraph{Simulation Parameters}
As a paradigmatic example, consider a dimer suspended in water ($n_p = 1.59, 
n_m = 1.33$) located at the focus of a Gaussian beam (more specifically a Laguerre-Gaussian beam of mode $[0,0]$), the beam is focused by a objective 
with numerical aperture of 1.2 and is x polarised. The size ratio of the two 
sphere's is given by $a_{I}/a_{II} = 2$ where $a_{I}$ is kept at $1\ \mu m$ 
unless specified otherwise; the dimer's orientation is given by a unit vector connecting the centres of both spheres, we define the 'standard' orientation 
as being aligned with the direction of beam propagation direction - and 
therefore the 'inverted' orientation is defined when the dimer is orientated 
against the direction of beam orientation (see figures~\ref{fig:paradigmatic}(b) 
and (d)).

@@

We repeated the same calculation but now while the dimer is in its 'inverted' orientation, instead of a single point where the optical force is minimised we 
see that there are instead two separate equilibrium positions, one above the focus
and one below the focus. In this particular example the two positions are far enough
apart that both can be considered as separate harmonic traps.    
\begin{figure}[h!]
	\centering
	\begin{subfigure}{.75\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=0.png}
		\caption{}
		\label{lam=2}
	\end{subfigure}\hfill % <-- "\hfill"
	\begin{subfigure}{.25\linewidth}
		\centering
		\raisebox{50pt}[0pt][0pt]{\makebox{}\includegraphics[width=0.3\linewidth, keepaspectratio]{theta=0.png}}
		\caption{}
		\label{large over small}
	\end{subfigure}
	\medskip
	\begin{subfigure}{.75\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=180.png}
		\caption{}
		\label{lam=2_inverted}
	\end{subfigure}\hfill % <-- "\hfill"
	\begin{subfigure}{.25\linewidth}
		\centering
		\raisebox{30pt}[0pt][0pt]{\makebox{}\includegraphics[width=0.3\linewidth, keepaspectratio]{theta=180.png}}
		\caption{}
		\label{small_over_large}
	\end{subfigure}
	\caption{Plots of force vs displacement of the centre of mass of 
		the dimer (µm) for the case of a dimer of size ratio 2. (a) is 
		the case where the dimer is in its' 'standard' orientation, where
		the dimer is trapped at $z = 1.71\ \mu m$. (c) is the case where 
		the dimer is in its' 'inverted' orientation, the dimer is trapped 
		at two positions: $z = 1.20\ \mu m$ \& $z=-1.63\ \mu m$. 
		(b) and (d) are renders to visualise the dimer orientation are shown 
		below each plot. The black lines on each force-curve is a linear 
		fit with the slope being reported as the trap stiffness in the legend.}
		\label{fig:paradigmatic}
\end{figure}

>>>>

\paragraph{Simulation Parameters}
As a paradigmatic example, consider a dimer suspended in water ($n_p = 1.59, 
n_m = 1.33$) located at the focus of a Gaussian beam (more specifically a Laguerre-Gaussian beam of mode $[0,0]$), the beam is focused by a objective 
with numerical aperture of 1.2 and is x polarised. The size ratio of the two 
sphere's is given by $a_{I}/a_{II} = 2$ where $a_{I}$ is kept at $1\ \mu m$ 
unless specified otherwise; the dimer's orientation is given by a unit vector connecting the centres of both spheres, we define the 'standard' orientation 
as being aligned with the direction of beam propagation direction - and 
therefore the 'inverted' orientation is defined when the dimer is orientated 
against the direction of beam orientation (see left hand side of figure~\ref{fig:paradigmatic}).

@@

We repeated the same calculation but now while the dimer is in its 'inverted' orientation, instead of a single point where the optical force is minimised we 
see that there are instead two separate equilibrium positions, one above the focus
and one below the focus. In this particular example the two positions are far enough
apart that both can be considered as separate harmonic traps.    
\begin{figure}[h!]
	\centering
	\begin{subfigure}{.65\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=0.png}
		\caption{}
		\label{lam=2}
	\end{subfigure}\hfill % <-- "\hfill"
	\begin{subfigure}{.25\linewidth}
		\centering
		\raisebox{0pt}[0pt][0pt]{\makebox{}\includegraphics[width=0.3\linewidth, keepaspectratio]{theta=0.png}}
		\label{large over small}
	\end{subfigure}
	\medskip
	\begin{subfigure}{.65\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=180.png}
		\caption{}
		\label{lam=2_inverted}
	\end{subfigure}\hfill % <-- "\hfill"
	\begin{subfigure}{.25\linewidth}
		\centering
		\raisebox{0pt}[0pt][0pt]{\makebox{}\includegraphics[width=0.3\linewidth, keepaspectratio]{theta=180.png}}
		\label{small_over_large}
	\end{subfigure}
	\caption{Plots of force vs displacement of the centre of mass of 
		the dimer (µm) for the case of a dimer of size ratio 2. (a) is 
		the case where the dimer is in its' 'standard' orientation, where
		the dimer is trapped at $z = 1.71\ \mu m$. (b) is the case where 
		the dimer is in its' 'inverted' orientation, the dimer is trapped 
		at two positions: $z = 1.20\ \mu m$ \& $z=-1.63\ \mu m$. 
		On the left are renders to visualise the dimer orientation are shown 
		below each plot. The black lines on each force-curve is a linear 
		fit with the slope being reported as the trap stiffness in the legend.}
		\label{fig:paradigmatic}
\end{figure}
